Cover Letter

### 2017-12-23 paper/sections/0_abstract.tex
paper: finish evaluation (#44, #38, #34, #33, #32, #27)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show 8\(\times\) speedup and 2\(\times\) scale when compared to our baseline
system.

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show similar speedups to related work \newcomment{(up to \(91.7\times\)
speedup) but more importantly, our prototype can custom fit subtrees in the
same namespace to applications common in large data centers, such as
checkpoint-restart (\(91.7\times\), user home directories (within a 0.03
standard deviation from optimal), and clients checking for partial results
(only a 2\% overhead).}  \oldcomment{ and can scale to 2\(\times\) as many
clients when compared to our baseline system.}

### 2017-12-23 paper/sections/1_introduction.tex
paper: finish evaluation (#44, #38, #34, #33, #32, #27)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that these techniques drastically improve performance (we see 104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many clients
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We use Ceph as a prototyping platform because it
is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

>>>>

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research of decoupled namespaces; specifically
that these techniques drastically improve performance.  We go a step further by
quantifying the costs of merging updates (3.37\(\times\) slow down) and
maintaining durability (\(2.4\times\) slow down).  In our prototype,
\newcomment{we also show how to assign subtree semantics for certain
applications such as checkpoint-restart (\(91.7\times\) speedup if consistency
is fully relaxed), user home directories (within a 0.03 standard deviation from
optimal), and clients checking for partial results (only a 2\% overhead).}
\oldcomment{we get an 8\(\times\) speedup and can scale to twice as many
clients when we assign a more relaxed form of consistency and durability to a
subtree with a create-heavy workload.}  We use Ceph as a prototyping platform
because it is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2017-12-23 paper/sections/6_results.tex
paper: finish evaluation (#44, #38, #34, #33, #32, #27)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application.  We scope the evaluation to one metadata server and scale the
number of parallel clients. This type of analysis shows the capacity and
performance of a metadata server with superior metadata protocols, which should
be used to inform load balancing across a metadata cluster. Load balancing
across a cluster of metadata servers with partitioning and replication can be
explored with something like Mantle~\cite{sevilla:sc15-mantle}.

@@

\newcomment{We run experiments on the same cluster and normalize results to
control for hardware differences and to make our results more generally
applicable. We use a CloudLab cluster of 34 nodes connected with 10Gbit
ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and SSDs.  Each node uses
Ubuntu 14.04 and we develop on Ceph's Jewel release, version 10.2.1, which was
released in May 2016. All daemons run as a single process (the default setting
for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.}

\newcomment{We understand concerns about cluster size and network, especially
for systems aimed at HPC but our evaluation focuses on verifying the behavior of
different techniques in the same global namespace. These techniques have
already proven to be effective and scalable in systems that specialize an
entire namespace according to a single optimization strategy (e.g., Lustre,
BatchFS, DeltaFS), so our evaluation explores the behavior of the
consistency/durability mechanisms and their effect with/without isolation.}

\newcomment{To make our results reproducible, this paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.
The source code is available on the Cudele
branch\footnote{\newcomment{https://github.com/michaelsevilla/ceph/tree/cudele}}
of our Ceph fork.} \addressesissue{1}

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
\newcomment{Overhead of processing 100K events for each mechanism in
Table~\ref{table:mechanisms}. Results are normalized to the runtime of writing
events to client memory. The bars on the far right show the overhead of
building consistency/durability semantics of real world systems.}
\oldcomment{Performance of each mechanism (left) and building the consistency/durability
semantics of real-world systems (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.}\label{fig:composable-mechanisms}}
\end{figure}

@@

Figure~\ref{fig:composable-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write 100K file create updates to the client's
in-memory journal ({\it i.e.} the Append Client Journal mechanism).
Stream is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  100K is the maximum recommended size of a directory in
CephFS; preliminary experiments with larger directory sizes show memory
problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures \oldcomment{have large
slowdowns}\newcomment{can slowdown performance by {\it orders of magnitude}}
for the larger number of creates. For example, RPCs has a \(90\times\) slowdown
because it relies on the internal CephFS directory data structures. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal) experience a much less drastic slowdown because
the journal data structure does not need to be scanned for every operation.
Events are written to the end of the journal without even checking the validity
({\it e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} RPCs is \(66\times\) slower than Volatile
Apply because sending individual metadata updates over the network is costly.
While RPCs sends a request for every file create, Volatile Apply
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (Nonvolatile Apply) is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of Nonvolatile Apply:} The cost of Nonvolatile
Apply is much larger than all the other mechanisms.  That mechanism was not
implemented as part of Cudele -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communicating through the object store is shown
by comparing the runtime of Volatile Apply + Global Persist to
Nonvolatile Apply. These two operations end up with the same final metadata
state but using Nonvolatile Apply is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing Local and Global
Persist demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The Global Persist
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the bandwidth of the object store can help mitigate the overheads of
globally persisting metadata updates.

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5KB. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data center networks are reasonable.

@@

@@

First we show how we can build application-specific subtrees by composing
mechanisms and that \oldcomment{this approach}\newcomment{coupling
well-established techniques to specific applications} results in a more a
scalable global namespace.  We start with clients creating files in private
directories because this workload is heavily studied in
HPC~\cite{weil:sc2004-dyn-metadata, ren:sc2014-indexfs, patil:fast2011-giga,
zheng:pdsw2014-batchfs, sevilla:sc15-mantle}, mostly due to
checkpoint-restart~\cite{bent_plfs_2009}.  But the workload also appears in
cloud workloads~\cite{xiao:socc15-shardfs}, where systems like Hadoop use the
file abstraction to exchange work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  The workload is clients creating 100K files
in private directories in the same global namespace.

@@

The graph on the right of Figure~\ref{fig:composable-mechanisms} shows how
applications can compose mechanisms together to get the consistency/durability
guarantees they need in a global namespace.  We label the \(x\)-axis with
systems that employ these semantics, as described in
Figure~\ref{fig:subtree-policies}.  Again, the runtime is normalized to
creating files in the client's in-memory journal.  We make no guarantees
during execution of the mechanisms or when transitioning semantics -- the
semantics are guaranteed {\it once the mechanism completes}. So if servers fail
during a mechanism, metadata or data may be lost.

@@

To show the contention at the metadata server, in Figure~\ref{fig:mergescale}
we scale the number of clients for the RPC per operation strategy and the
decoupled namespace strategy. For RPCs, we increase the number of clients
making requests to the metadata server and for decoupled we increase the number
of concurrent clients operating in parallel. So for the 30 clients data point,
we are measuring the operations per second for 30 client journals that land on
the metadata server at the same time. The ``create + merge" bar adds the time
it takes for clients to generate the journal of events in parallel. The
experiment is run three times but the standard deviation is too small to see.

@@

This workload scales further with decoupled namespaces because the metadata
server is not overwhelmed with RPC requests. Compared to
Figure~\ref{fig:overhead-c} we can scale to 40 clients which is more than
double the capacity of a single metadata server using the RPC strategy to
maintain strong consistency\footnote{\newcomment{Note that for the 20 clients
bar in Figure~\ref{fig:mergescale}, we plot the throughput for using 18 clients
(the maximum number of clients supported by RPCs)}}. Related work has pointed
to on-disk metadata format as the primary factor for improved scalability; but
our results show that the weakened consistency and durability enables the
scalability improvements. The on-disk metadata formats in this experiment are
the same for all schemes.

The performance of decoupled namespaces is better than RPCs because we place no
restrictions on the validity of metadata inserted into the journal and avoid
touching poorly scaling data structures. We can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files
({\it i.e.} only append \texttt{open()} requests to the journal).  When the
updates are merged by the metadata server into the in-memory metadata store
they never scan growing data structures.  Had we implemented the Append Client
Journal mechanism to include \texttt{lookup()} commands before \texttt{open()}
requests, we would have seen the poor scaling that we see with the RPCs
mechanism.

%% DeltaFS vs. BatchFS vs. POSIX IO: decoupled is faster
%% (5-7x) vs. (90-104x) slower
%% Does not scale?
%% Strong Consistency > 10X slower than Weak Consistency 
%{\it Speedups of Decoupled Namespaces:} Weak consistency uses the
%decoupled namespace strategy and shows up to a \(20\times\) speedup over the
%traditional namespaces that use RPCs. Compared to the baseline the slowdown is
%\(5-7\times\) for Strong Consistency, which emulates BatchFS and
%\(90-104\times\) for Weak Consistency, which emulates DeltaFS.

%{\it Durability \(<<\) Consistency:} The performance of these semantics
%suggests that the overhead of consistency is much larger than the overhead of
%durability. This conclusion should be stronger as we scale the number of files
%because the cost of streaming the journal into the object store is constant.
%
% Weak Consistency benefit not due to metadata format

@@

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.
C}lients create files in private directories while another client interferes by
creating \oldcomment{more}\newcomment{1000} files in each directory. This
introduces false sharing and the metadata server revokes capabilities on
directories touched by the interfering client. While HPC tries to avoid these
situations with workflows~\cite{zheng:pdsw2014-batchfs,
zheng:pdsw2015-deltafs}, it still happens in distributed file systems when
users unintentionally access directories in a shared file system.
\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}

@@

\oldcomment{We draw three conclusions: (1) clients that use the API to block interfering
clients  get the same performance as isolated clients, (2) there is a
negligible effect on performance for the extra work the metadata server does to
return \texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
negligible effect on performance.

\textbf{Takeaway}: the API lets users isolate directories when applications
need better and more reliable performance. Blocking updates is an effective way of
controlling consistency.}

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics\newcomment{ to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache} . The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help users judge
the progress of their jobs, Cudele clients have a ``namespace sync" that sends
batches of updates back to the global namespace at regular intervals.

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to a decoupled namespace and
pausing to send updates to the metadata server. The error bars are the standard
deviations of 3 runs. We scale the namespace sync interval to show the
trade-off of frequently pausing or writing large logs of updates.  We use an
idle core to log the updates and to do the network transfer. The client only
pauses to fork off a background process, which is expensive as the address
space needs to copied. The alternative is to pause the client completely and
write the update to disk but since this implementation is limited by the speed
of the disk, we choose the memory-to-memory copy of the fork approach.

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds because larger intervals must write more updates to
disk and network. For the 25 second interval, the client only pauses 3-4 times
but each sync writes about 278 thousand updates at once, which is a 678MB
journal.

>>>>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application.  \newcomment{These techniques have already proven to be
effective and scalable in systems that specialize an entire namespace according
to a single optimization strategy (e.g., Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with/without isolation.}

\newcomment{\indent We run experiments on the same cluster and graph the
standard deviations for three runs (sometimes error bars are too small to see).
We also normalize results to control for hardware differences and to make our
results more generally applicable. We use a CloudLab cluster of 34 nodes
connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and SSDs.
Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel release, version
10.2.1, which was released in May 2016. All daemons run as a single process
(the default setting for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.} We scope the
evaluation to one metadata server and scale the number of parallel
clients\newcomment{ each doing 100K operations}\footnote{This is the maximum
recommended size of a directory in CephFS; preliminary experiments with larger
directory sizes show memory problems.}. This type of analysis shows the
capacity and performance of a metadata server with superior metadata protocols,
which should be used to inform load balancing across a metadata cluster. Load
balancing across a cluster of metadata servers with partitioning and
replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.

\newcomment{\indent To make our results reproducible, this paper adheres to The
Popper Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.
The source code is available on the Cudele
branch\footnote{\newcomment{https://github.com/michaelsevilla/ceph/tree/cudele}}
of our Ceph fork.} \addressesissue{1}

%\newcomment{\indent We understand concerns about cluster size and network, especially
%for systems aimed at HPC but our evaluation focuses on verifying the behavior
%of different techniques in the same global namespace.

@@

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
\newcomment{Overhead of processing 100K create events for each mechanism in
Table~\ref{table:mechanisms}. Results are normalized to the runtime of writing
events to client memory. The bars on the far right show the overhead of
building consistency/durability semantics of real world systems.}
\oldcomment{Performance of each mechanism (left) and building the consistency/durability
semantics of real-world systems (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.}\label{fig:composable-mechanisms}}
\end{figure}

@@

\oldcomment{Figure~\ref{fig:composable-mechanisms} shows the runtime of the
Cudele mechanisms for a single client creating files in the same directory, }
\newcomment{We measure the overhead of each mechanism by having 1 client create
100K files in a directory for various subtree configurations.
Figure~\ref{fig:composable-mechanisms} shows the time that it takes each Cudele
mechanism to process all metadata events.  Results are} normalized to the time
it takes to write 100K file create updates to the client's in-memory journal
({\it i.e.} the Append Client Journal mechanism).  \newcomment{The first graph
groups the consistency mechanisms, the second groups the durability mechanisms,
and the third has compositions representing real-world systems.} Stream is an
approximation of the overhead and is calculated by subtracting the runtime of
the job with the journal turned off from the runtime with the journal turned
on.  \oldcomment{100K is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.}

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large
slowdowns\oldcomment{ for the larger number of creates}. For example, RPCs has
a \oldcomment{\(90\times\)}\newcomment{\(18\times\)} slowdown because this
technique relies on the internal directory data structures. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal experience a much less drastic slowdown because the journal
data structure does not need to be scanned for every operation.  Events are
written to the end of the journal without even checking the validity ({\it
e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} RPCs is
\oldcomment{\(66\times\)}\newcomment{\(19.9\times\)} slower than Volatile Apply
because sending individual metadata updates over the network is costly.  While
RPCs sends a request for every file create, Volatile Apply \oldcomment{writes
all the updates to the in-memory journal and applies them}\newcomment{writes
directly} to the in-memory data structures in the metadata server. While
communicating the decoupled namespace directly to the metadata server
\newcomment{with Volatile Apply} is faster, communicating through the object
store \newcomment{with Nonvolatile Apply} is
\oldcomment{\(10\times\)}\newcomment{\(78\times\)} slower.

% TODO: why is apply so slow.  apply: no CephFS changes, pulls/pushes same
% RADOS obj.  v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of Nonvolatile Apply:} The cost of Nonvolatile Apply is much
larger than all the other mechanisms.  That mechanism was not implemented as
part of Cudele -- it was a debugging and recovery tool packaged with CephFS. It
works by iterating over the updates in the journal and pulling all objects that
{\it may} be affected by the update.  This means that two objects are
repeatedly pulled, updated, and pushed: the object that houses the experiment
directory and the object that contains the root directory ({\it i.e.},
\texttt{/}).  The cost of communicating through the object store is shown by
comparing the runtime of Volatile Apply + Global Persist
\newcomment{(\(1.3\times\))} to Nonvolatile Apply\newcomment{ (\(78\times\))}.
These two operations end up with the same final metadata state but using
Nonvolatile Apply is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} \newcomment{Stream has the highest
slowdown at \(2.4\times\) because the overhead of maintaining and streaming the
journal is incurred by the metadata server}.  Comparing Local and Global
Persist demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The Global Persist performance is \newcomment{only
\(0.2\times\) slower than Local Persist because Global
Persist}\oldcomment{\(1.5\times\) faster because the object store} is
leveraging the collective bandwidth of the disks in the cluster. This benefit
comes from the object store itself but should be acknowledged when making
decisions for the application; the bandwidth of the object store can help
mitigate the overheads of globally persisting metadata updates. The storage per
journal update is about 2.5KB. So the storage footprint scales linearly with
the number of metadata creates and suggests that updates for a million files
would be \newcomment{2.38GB}\oldcomment{2.5KB \(*\) 1 million files \(=\)
2.38GB. Transfer times for payloads of this size in most HPC/data center
networks are reasonable.}

@@

\newcomment{{\it Composing Mechanisms}: The graph on the right of
Figure~\ref{fig:composable-mechanisms} shows how applications can compose
mechanisms together to get the consistency/durability guarantees they need in a
global namespace.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  Again, the
runtime is normalized to creating files in the client's in-memory journal.  We
make no guarantees during execution of the mechanisms or when transitioning
semantics -- the semantics are guaranteed {\it once the mechanism completes}.
So if servers fail during a mechanism, metadata or data may be lost. This graph
shows how we can build application-specific subtrees by composing mechanisms
and that coupling well-established techniques to specific applications results
in a more scalable global namespace.}

@@

\oldcomment{Next we show how we can build application-specific subtrees by composing
mechanisms and that \oldcomment{this approach}\newcomment{coupling
well-established techniques to specific applications} results in a more a
scalable global namespace.  }

We start with clients creating files in private directories because this
workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads~\cite{xiao:socc15-shardfs},
where systems like Hadoop use the file abstraction to exchange work units to
workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}. \oldcomment{ The workload is clients creating 100K files
in private directories in the same global namespace. }

@@

\oldcomment{The graph on the right of Figure~\ref{fig:composable-mechanisms} shows how
applications can compose mechanisms together to get the consistency/durability
guarantees they need in a global namespace.  We label the \(x\)-axis with
systems that employ these semantics, as described in
Figure~\ref{fig:subtree-policies}.  Again, the runtime is normalized to
creating files in the client's in-memory journal.  We make no guarantees
during execution of the mechanisms or when transitioning semantics -- the
semantics are guaranteed {\it once the mechanism completes}. So if servers fail
during a mechanism, metadata or data may be lost.}

@@

\oldcomment{To show the contention at the metadata server, }In
Figure~\ref{fig:mergescale} we scale the number of clients \newcomment{each
doing 100K file creates in their own directories for three types of subtrees:
one with strong consistency and global durability (RPCs), one with invisible
consistency and local durability (decoupled: create), and one with weak
consistency and local durability (decoupled: create + merge). Results are
normalized to 1 client that creates 100K files using RPCs (about 549
creates/sec). As opposed to earlier graphs in
Section~\S\ref{sec:posix-overheads} that plotted the throughput of the slowest
client, Figure~\ref{fig:mergescale} plots the throughput from the perspective
of the metadata server. Plotting this way is easier to understand because of
how we normalize but the speedups over the RPC approach are the same, whether
we look at the slowest client or not.}

\newcomment{When the metadata server is operating at peak efficiency between 5
and 20 clients, ``decoupled: merge + create" outperforms ``RPCs" by
\(3.37\times\) because ``decoupled: merge + create" uses a relaxed form of
consistency and leverages bulk updates just liked
DeltaFS~\cite{zheng:pdsw2015-deltafs}.  The ``RPCs" and ``decoupled: merge +
create" curves flatten out at a slowdown of \(4.5\times\) and \(15\times\),
respectively, because more clients increases the load at the metadata server.
Alternatively, the ``decoupled: create" curve scales linearly with the number
of concurrent clients because clients operate in parallel and write updates
locally. At 20 clients, we observe a \(91.7\times\) speedup for ``decoupled:
create" over RPCs.}\oldcomment{ for the RPC per operation strategy and the
decoupled namespace strategy.  For RPCs, scaling the number of clients
increases the load on the metadata server and for decoupled we increase the
number of concurrent clients operating in parallel.  Related work has pointed
to on-disk metadata format as the primary factor for improved scalability; but
our results show that the weakened consistency and durability enables the
scalability improvements. The on-disk metadata formats in this experiment are
the same for all schemes.}

\newcomment{Another reason that} the performance of decoupled namespaces is
better than RPCs \newcomment{is because decoupled namespaces (1)} place no
restrictions on the validity of metadata inserted into the journal and
\newcomment{(2)} avoid touching poorly scaling data structures. We can scale
linearly if we weaken our consistency by never checking for the existence of
files before creating files ({\it i.e.} only append \texttt{open()} requests to
the journal).  When the updates are merged by the metadata server into the
in-memory metadata store they never scan growing data structures.  Had we
implemented the \oldcomment{Append Client Journal mechanism}\newcomment{client}
to include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen the poor scaling \newcomment{behavior} that we see with the RPCs
mechanism.

\newcomment{One final point about the ``decoupled: merge + create" curve is
that the results in the graph are pessimistic. They model a scenario in which
all client journals arrive at the same time.} So for the 20 clients data point,
we are measuring the operations per second for 20 client journals that land on
the metadata server at the same time. \newcomment{Had we added infrastructure
to overlay journal arrivals or time client sync intervales, we could have
scaled more closely to ``decoupled: create".}\oldcomment{The ``create + merge"
bar adds the time it takes for clients to generate the journal of events in
parallel. ALSO DISCUSS 3.7X!!}

@@

\oldcomment{This workload scales further with decoupled namespaces because the metadata
server is not overwhelmed with RPC requests. Compared to
Figure~\ref{fig:overhead-c} we can scale to 40 clients which is more than
double the capacity of a single metadata server using the RPC strategy to
maintain strong consistency Note that for the 20 clients
bar in Figure~\ref{fig:mergescale}, we plot the throughput for using 18 clients
(the maximum number of clients supported by RPCs). }

@@

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.
C}lients create 100K files in their own directories while another client interferes by
creating \oldcomment{more}\newcomment{1000} files in each directory. This
introduces false sharing and the metadata server revokes capabilities on
directories touched by the interfering client. While HPC tries to avoid these
situations with workflows~\cite{zheng:pdsw2014-batchfs,
zheng:pdsw2015-deltafs}, it still happens in distributed file systems when
users unintentionally access directories in a shared file system.
\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}

@@

\oldcomment{We draw three conclusions: (1) clients that use the API to block interfering
clients  get the same performance as isolated clients, (2) there is a
negligible effect on performance for the extra work the metadata server does to
return \texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
negligible effect on performance.}

\oldcomment{\textbf{Takeaway}: the API lets users isolate directories when applications
need better and more reliable performance. Blocking updates is an effective way of
controlling consistency.}

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help users judge
the progress of their jobs, Cudele clients have a ``namespace sync" that sends
batches of updates back to the global namespace at regular intervals.

% Does this implementation need to be described in the implementation?
\newcomment{We configure a subtree as a decoupled namespace with invisible
consistency, local durability, and partial updates enabled.}
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to the decoupled namespace and
pausing to send updates to the metadata server. \oldcomment{The error bars are
the standard deviations of 3 runs.} We scale the namespace sync interval to
show the trade-off of frequently pausing or writing large logs of updates.  We
use an idle core to log the updates and to do the network transfer. The client
only pauses to fork off a background process, which is expensive as the address
space needs to be copied. The alternative is to pause the client completely and
write the update to disk but since this implementation is limited by the speed
of the disk, we choose the memory-to-memory copy of the fork approach.

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead), because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a 678MB journal.
